Constraint Programming - Inside Gecode

### 2014-05-06 paper.tex
addd bibitem
added reference

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:linearConstraint}, \refeq{eq:allDifferent} and \refeq{eq:trailingZero} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. This example contains only linear constraints and could therefore be solved through linear programming REFERENCE MISSING. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design and robotics \cite[p.~221]{trendsInCP}.

@@

	\begin{thebibliography}{1}
		\bibitem{handbookCP}
		F.~Rossi, P.~van~Beek and T.~Walsh, \emph{Handbook of Constraint Programming}, Amsterdam, The Netherlands: Elsevier, 2006, ISBN: 978-0-444-52726-4
		\bibitem{allDifferent}
		W.~van~Hoeve, \emph{The Alldifferent Constraint: A Survey}, http://www.andrew.cmu.edu/user/vanhoeve/papers/alldiff.pdf
		\bibitem{trendsInCP}
		F.~Benhamou, N.~Jussien, B.~A.~O'Sullivan, \emph{Trends in Constraint Programming}, Wiley-ISTE, 2007, ISBN: 978-1-905209-97-2
		\bibitem{gecode}
		http://www.gecode.org/
		\bibitem{programmingGecode}
		C.~Schulte, G.~Tack and M.~Z.~Lagerkvist, \emph{Modeling and Programming with Gecode}, http://www.gecode.org/doc-latest/MPG.pdf
		\bibitem{limitedDiscrepancy}
		W.~D.~Harvey, M.~L.~Ginsberg, \emph{Limited Discrepancy Search}, Morgan Kaufmann, 1995
	\end{thebibliography}
\end{document}

>>>>

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:linearConstraint}, \refeq{eq:allDifferent} and \refeq{eq:trailingZero} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. This example contains only linear constraints and could therefore be solved through linear programming \cite[1]{linearProgramming}. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design and robotics \cite[p.~221]{trendsInCP}.

@@

	\begin{thebibliography}{1}
		\bibitem{handbookCP}
		F.~Rossi, P.~van~Beek and T.~Walsh, \emph{Handbook of Constraint Programming}, Amsterdam, The Netherlands: Elsevier, 2006, ISBN: 978-0-444-52726-4
		\bibitem{allDifferent}
		W.~van~Hoeve, \emph{The Alldifferent Constraint: A Survey}, http://www.andrew.cmu.edu/user/vanhoeve/papers/alldiff.pdf
		\bibitem{trendsInCP}
		F.~Benhamou, N.~Jussien, B.~A.~O'Sullivan, \emph{Trends in Constraint Programming}, Wiley-ISTE, 2007, ISBN: 978-1-905209-97-2
		\bibitem{gecode}
		http://www.gecode.org/
		\bibitem{programmingGecode}
		C.~Schulte, G.~Tack and M.~Z.~Lagerkvist, \emph{Modeling and Programming with Gecode}, http://www.gecode.org/doc-latest/MPG.pdf
		\bibitem{limitedDiscrepancy}
		W.~D.~Harvey, M.~L.~Ginsberg, \emph{Limited Discrepancy Search}, Morgan Kaufmann, 1995
		\bibitem{linearProgramming}
		L.~Cooper and D.~Steinberg, \emph{Methods and Applications of Linear Programming}, W.~B.~Saunder~Company, 1974, ISBN: 0-7216-2694-7
	\end{thebibliography}
\end{document}
